---
title: "Data Science Week 1"
format: html
editor: visual
---

---
title: "Data Science Week 1"
format: html
editor: visual
---

## Data Science Questions

1.  What do you think being a **data scientist** is about?\
    Data Scientists translate raw data into understanding and insight. The work may start as discovery and exploration. Machine learning methods, data visualization and storytelling are often employed. According to *Practitioner's Guide to Data Science* by Lin and Li, data scientists perform engineering, analysis, and modeling/inference.

2.  What are the differences/similarities between **data scientists** and **statisticians**?\
    \
    Differences:

    -   Data scientists focus more on exploring complex business problems

    -   Data scientists focus more on machine learning methods and prediction

    -   Data scientists tend to deal with larger data sets and require experience cleaning and manipulating data

    -   Statisticians focus more on mathematical problems

    -   Statisticians tend to follow the scientific method and hypothesis testing

    Similarities:

    -   Both use descriptive and inferential statistics
    -   Both tend have had extensive coursework in statistics, and, at the very least, require deep understanding of statistical methods

3.  How do I consider myself in relation to these two areas?\
    At this point in my professional career, I have a bit more experience in statistical methods to address marketing research and UX research questions. From an academic perspective, I have more recently focused on data science, but have not had the opportunity to apply those skills in a professional capacity.

## Initial Code

Set `y` to represent the kernel density of petal width in the `iris` dataset

```{r}
y <- density(iris$Petal.Width)
```

Create an `R code` chunk to determine the `class`, `type`, and `structure` of the object `y`

```{r}
class(y)
typeof(y)
str(y)
```

Create an `R code` chunk that uses the `plot` function on `y`. Hide the `R code` in the final document by setting echo to false

```{r}
#| echo: false

plot(y)
```
